### 2014-01-14 thesis-proposal/problem.tex
Done sections 1 and 2 of proposal

If new languages only include constructs that can already be expressed safely and reasonably naturally in the common language, then this approach can work well.
But many of the most innovative constructs found in modern languages (often, the features that justify their creation) are difficult to define in terms of existing constructs in ways that guarantee all necessary invariants are statically maintained and that do not require large amounts boilerplate code and run-time overhead. For example, the type system of F\# guarantees that null values cannot occur within F\# data structures, but maintaining this important invariant still requires run-time checks because the typing rules of F\# do not apply when F\# code is called from other languages on the Common Language Infrastructure (CLI) like C\#. The F\# type system also includes support for checking that units of measure are used correctly \cite{syme2012expert, kennedy1994dimension}, but this specialized invariant is left completely unchecked at language boundaries. 
%In Scala, traits that have default method implementations are difficult to implement from Java or other JVM languages and the workaround can break if the trait is modified \cite{scalatraitinterop}. 
In some cases, desirable features must be omitted entirely due to concerns about  interoperability. F\#, for example, is based on Ocaml, but due to the need for bidirectional interoperability with CLI languages, it cannot support features like polymorphic variants, modules or functors \cite{ocaml-manual}.
%\end{itemize}

>>>>

If new languages only include constructs that can already be expressed safely and reasonably naturally in the common language, then this approach can work well.
But many of the most innovative constructs found in modern languages (often, the features that justify their creation) are difficult to define in terms of existing constructs in ways that guarantee all necessary invariants are statically maintained and that do not require large amounts boilerplate code and run-time overhead. For example, the type system of F\# guarantees that null values cannot occur within F\# data structures, but maintaining this important invariant still requires run-time checks because the typing rules of F\# do not apply when F\# code is called from other languages on the Common Language Infrastructure (CLI) like C\#. The F\# type system also includes support for checking that units of measure are used correctly \cite{syme2012expert, kennedy1994dimension}, but this specialized invariant is left completely unchecked at language boundaries. 
%In Scala, traits that have default method implementations are difficult to implement from Java or other JVM languages and the workaround can break if the trait is modified \cite{scalatraitinterop}. 
In some cases, desirable features must be omitted entirely due to concerns about  interoperability. F\#, for example, is based on Ocaml, but due to the need for bidirectional interoperability with CLI languages, it cannot support features like polymorphic variants, modules or functors \cite{ocaml-manual} because they have no straightforward analogs in the object-oriented intermediate language of the CLI.
%\end{itemize}
